### 2014-12-31 paper_10_intro.tex
adding some more papers

\subsubsection{SOFTWARE QUALITY}
Quality is tested in \cite{Miguel2014}

\subsubsection{SOFTWARE ANALYTICS}
What is software analytics?

>>>>

\subsubsection{SOFTWARE QUALITY}
Quality is tested in \cite{Miguel2014} and a stack of other papers

\subsubsection{SOFTWARE ANALYTICS}
One area of research that is focusing on the evaluation of software development organizations
is \textit{software analytics}.  It is less focused o evaluation
and more so on analysis of software data.  The goal of software analytics is to extract insights
from software artifacts to aide practioners in making better decisions regarding software
development \cite{Zhang2013}.  The main focus areas of software analytics are:
\begin{description}
    \item[User Experience] - How can the software enable the user to more easily or quickly 
        accomplish the task at hand?
    \item[Quality] - How can the number of problems with the software be decreased?
    \item[Development Productivity] - How can the processes or tools be modified to increase 
        the rate at which software is produced? 
\end{description}

Martin Shepperd in \cite{Hassan2013} identified 3 important questions that software
analytics must address:
\begin{enumerate}
    \item ``How much better is my model performing than a naive strategy, such as guessing [\ldots]?''
    \item ``How practically significant are the results?''
    \item ``How sensitive are the results to small changes in one or more of the inputs?''
\end{enumerate}
These are 3 important questions that should be addressed when presenting any results in
software analytics.

### 2014-12-31 paper_20_sdo.tex
adding some more papers

\subsection{WHAT IS SOFTWARE ENGINEERING?}
    \textit{Software Engineering} as a term dates back to the 
    1968 North Atlantic Treaty Organization (NATO) conference \cite{Tsui2013, Naur1969}. Over the 
    years many definitions have been provided.  IEEE provides a definition that encompasses many of the
    other definitions.  IEEE defines software engineering as, 
    ''The application of a systematic, disciplined, quantifiable approach to the development, operation, and maintenance of software''
    \cite{Ieee1990}.

>>>>

\subsection{WHAT IS SOFTWARE ENGINEERING?}
    \textit{Software Engineering} as a term dates back to the 
    1968 North Atlantic Treaty Organization (NATO) conference \cite{Tsui2013, Naur1969}. Over the 
    years many definitions have been provided.  IEEE provides a definition that encompasses many of the
    other definitions.  IEEE ISO610.12 defines software engineering as, 
    ''The application of a systematic, disciplined, quantifiable approach to the development, operation, and maintenance of software''
    \cite{Ieee1990}.
